Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-22 manuscript/climate_sensitivity_draft.Rmd
Updated word_doc for #147 to include references

---
title: ""
author: ""
output:
  pdf_document:
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
link-citations: yes
biblio-style: "apalike"
csl: new-phytologist.csl
header-includes:
- \usepackage{setspace}\onehalfspacing
- \usepackage{lineno}
- \linenumbers
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

>>>>

---
title: ""
author: ""
output: word_document
  # pdf_document:
    # fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
link-citations: yes
biblio-style: "apalike"
csl: new-phytologist.csl
header-includes:
- \usepackage{setspace}\onehalfspacing
- \usepackage{lineno}
- \linenumbers
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---
